RDF Constraint Types to Validate Metadata \\ on Highly-Complex Person-Level and Aggregated Data

### 2015-04-08 paper/paper7/paper7-appendix.tex
evaluation

\textbf{Content-Driven Validation / Data Model Consistency}.
Is the data consistent with the intended semantics of the data model?
Such validation rules ensure the integrity of the data according to the data model.

\textbf{Technology-Driven Validation}.
Some validation rules can be generated automatically out of the defined data model, such as cardinality restrictions, universal quantifications, domains, ranges.

@@

\begin{itemize}
  \item Constraint types marked with an asterisk (*) can be used as OWL 2 axioms. Thus, reasoners may be used to infer implicit triples resolving constraint violations caused when these constraints are validated.
	\item \underline{Underlined subsections} are data model specific constraint types and do not correspond to RDF validation requirements (constraint types).
%	\item \underline{Underlined constraints} are part of content-driven validation.
%	\item \udash{Dashed underlined constraints} are part of technology-driven validation.
\end{itemize}

@@

\begin{itemize}
	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-01}}: 
	are compared variables represented in a compatible way, i.e. are the variables' code lists theoretically comparable?
		\begin{itemize}
		\item severity level: WARNING
	\end{itemize}
	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-02}}: 
	are variable definitions (\emph{dcterms:description}) available for each variable (\emph{disco:Variable}) to compare?
		\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-03}}:
	are code lists structured properly for each variable (\emph{disco:Variable}) to compare?
		\begin{itemize}
		\item severity level: WARNING
	\end{itemize}
	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-04}}:
	is for each code (for each variable (\emph{disco:Variable}) to compare) an associated category (a human-readable label) specified?
		\begin{itemize}
		\item severity level: INFO
	\end{itemize}
	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-05}}:
	each (\emph{disco:Variable}) to compare must be present.
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
\end{itemize}

@@

@@

	\item \textbf{{\em SKOS-C-DATA-MODEL-CONSISTENCY-01\footnote{Corresponds to qSKOS Quality Issues - SKOS Semi-Formal Consistency Issues - Relation Clashes}:}}
	Relation Clashes:
  Covers condition S27 from the SKOS reference document, that has not been defined formally. 
	\begin{itemize}
	  \item Implementation:
		In a first step, all pairs of concepts are found that are associatively connected, using a SPARQL query. In the second step, a graph is created, containing only hierarchically related concepts and the respective relations. For each concept pair from the first step, we check for a path in the graph from step two. If such a path is found, a clash has been identified and the causing concepts are returned. 
		\item Severity level: 
	\end{itemize}

	\item \textbf{{\em SKOS-C-DATA-MODEL-CONSISTENCY-02\footnote{Corresponds to qSKOS Quality Issues - SKOS Semi-Formal Consistency Issues - Mapping Clashes}:}}
	Mapping Clashes:
  Covers condition S46 from the SKOS reference document, that has not been defined formally. 
	\begin{itemize}
	  \item Implementation:
		Can be solved by issuing a SPARQL query. 
		\item Severity level: 
	\end{itemize}

	\item \textbf{{\em SKOS-C-DATA-MODEL-CONSISTENCY-03\footnote{Corresponds to qSKOS Quality Issues - SKOS Semi-Formal Consistency Issues - Mapping Relations Misuse}:}}
	Mapping Relations Misuse:
  According to the SKOS reference documentation, mapping relations (e.g., \emph{skos:broadMatch} or \emph{skos:relatedMatch}) should be asserted to concepts being members of different concept schemes. This check finds concepts that are related by a mapping property and are either members of the same concept scheme or members of no concept scheme at all. 
	\begin{itemize}
		\item Severity level: 
	\end{itemize}

@@

\subsection{Subsumption*}

@@

\begin{itemize}
	\item \textbf{{\em DISCO-C-SUBSUMPTION-01:}} 
All {\em disco:Universe}s must also be {\em skos:Concept}s (\ms{Universe $\sqsubseteq$ Concept}).
\end{itemize}

\subsection{Class Equivalence*}

@@

\begin{itemize}
	\item \textbf{{\em DISCO-C-CLASS-EQUIVALENCE-01:}}
All {\em sio:SIO\_000367} resources must also be {\em disco:Variable}s (\ms{Variable $\equiv$ SIO\_000367}).
The Semanticscience Integrated Ontology (SIO)\footnote{https://code.google.com/p/semanticscience/wiki/SIO} provides a simple, integrated ontology of types and relations for rich description of objects, processes and their attributes.
{\em sio:SIO\_000367} is a variable defined as a value that may change within the scope of a given problem or set of operations.
Thus, {\em sio:SIO\_000367} is equivalent to {\em disco:Variable}.
\end{itemize}

\subsection{Sub Properties*}

@@

\begin{itemize}
	\item \textbf{{\em DISCO-C-SUB-PROPERTIES-01:}}
If an individual \emph{x} is connected by {\em disco:fundedBy} to an individual \emph{y}, then \emph{x} is also connected by {\em dcterms:contributor} to \emph{y} (\ms{fundedBy $\sqsubseteq$ contributor}). 
\end{itemize}

\subsection{Property Domains*}

@@

\subsection{Property Ranges*}

@@

\begin{itemize}
	\item \textbf{{\em DISCO-C-INVERSE-OBJECT-PROPERTIES-01}}:
	\emph{disco:CategoryStatistics} resources are accessed from codes (\emph{skos:Concept}s) via \emph{disco:statisticsCategory}$^{-}$.
	\item \textbf{{\em DISCO-C-INVERSE-OBJECT-PROPERTIES-02}}:
	\emph{disco:SummaryStatistics} resources are accessed from \emph{disco:Variable}s via \emph{disco:statisticsVariable}$^{-}$.
	\item \textbf{{\em DISCO-C-INVERSE-OBJECT-PROPERTIES-03}}:
	\emph{disco:Variable}s are accessed from \emph{disco:Question}s via \emph{disco:question}$^{-}$.
\end{itemize}

@@

\subsection{Asymmetric Object Properties*}

@@

\begin{itemize}
	\item \textbf{{\em DISCO-C-ASYMMETRIC-OBJECT-PROPERTIES-01:}} 
A {\em disco:Variable} may be based on a {\em disco:RepresentedVariable}.
A {\em disco:RepresentedVariable}, however, cannot be based on a {\em disco:Variable}.
This is a kind of mistake which may occur as a semantically equivalent object property for the other direction may also be possible ({\em disco:basisOf}) (\ms{$basedOn \sqcap basedOn^{-} \sqsubseteq \bot$}).
\end{itemize}

@@

\begin{itemize}
  \item \textbf{{\em DISCO-C-IRREFLEXIVE-OBJECT-PROPERTIES-01:}}
	In \emph{Disco}, every object property is irreflexive.
  No individual is connected by the object property {\em instrument} to itself (\ms{$\top$ $\sqsubseteq$ $\neg$ $\exists  instrument . Self$}).
\end{itemize}

@@

\begin{itemize}
  \item \textbf{{\em DISCO-C-CLASS-SPECIFIC-IRREFLEXIVE-OBJECT-PROPERTIES-01:}}
Within the Disco context, {\em skos:Concept}s cannot be related via the object property {\em skos:boader} to themselves (\ms{Concept $\sqsubseteq$ $\neg$$\exists$ broader.Self.}). 
	\item \textbf{{\em DISCO-C-CLASS-SPECIFIC-IRREFLEXIVE-OBJECT-PROPERTIES-02:}}
Within the Disco context, {\em skos:Concept}s cannot be related via the object property {\em skos:narrower} to themselves (\ms{Concept $\sqsubseteq$ $\neg$$\exists$ narrower.Self.}). 
\end{itemize}

\subsection{Disjoint Properties}

@@

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-DISJOINT-PROPERTIES-01:}} 
	All \emph{Data Cube} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
  The properties \emph{qb:dataSet} and \emph{qb:structure} are disjoint ($dataSet \sqsubseteq \neg structure$).
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DCAT-C-DISJOINT-PROPERTIES-01:}} 
	All \emph{DCAT} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DISCO-C-DISJOINT-PROPERTIES-01:}} 
	All \emph{Disco} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
  The properties \emph{disco:variable} and \emph{disco:question} are disjoint ($variable \sqsubseteq \neg question$).
\end{itemize}

\begin{itemize}
	\item \textbf{{\em PHDD-C-DISJOINT-PROPERTIES-01:}} 
	All \emph{PHDD} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
	The properties \emph{phdd:isStructuredBy} and \emph{phdd:column} are disjoint ($isStructuredBy \sqsubseteq \neg column$)
\end{itemize}

@@

	\item \textbf{{\em SKOS-C-DISJOINT-PROPERTIES-01:}} 
	All \emph{SKOS} properties (not having the same domain and range classes) are defined to be pairwise disjoint.

	\item \textbf{{\em SKOS-C-DISJOINT-PROPERTIES-02\footnote{Corresponds to qSKOS Quality Issues - SKOS Semi-Formal Consistency Issues - Disjoint Labels Violation}:}}
	Disjoint Labels Violation:
  Covers condition S13 from the SKOS reference document stating that "\emph{skos:prefLabel}, \emph{skos:altLabel} and \emph{skos:hiddenLabel} are pairwise disjoint properties". 
	\begin{itemize}
	  \item Implementation:
		A SPARQL query collects all labels of all concepts, building an in-memory structure. This structure is then checked for disjoint entries. 
		\item Severity level: 
	\end{itemize}

@@

\begin{itemize}
	\item \textbf{{\em XKOS-C-DISJOINT-PROPERTIES-01:}} 
	All \emph{XKOS} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
\end{itemize}

\subsection{Disjoint Classes}

@@

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-DISJOINT-CLASSES-01:}} 
All \emph{Data Cube} classes are defined to be pairwise disjoint.
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DCAT-C-DISJOINT-CLASSES-01:}} 
All \emph{DCAT} classes are defined to be pairwise disjoint.
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DISCO-C-DISJOINT-CLASSES-01:}} 
All \emph{Disco} classes are defined to be pairwise disjoint (e.g. \ms{Study $\sqcap$ Variable $\sqsubseteq$ $\perp$}).
\end{itemize}

\begin{itemize}
	\item \textbf{{\em PHDD-C-DISJOINT-CLASSES-01:}} 
All \emph{PHDD} classes are defined to be pairwise disjoint.
\end{itemize}

\begin{itemize}
	\item \textbf{{\em SKOS-C-DISJOINT-CLASSES-01:}} 
All \emph{SKOS} classes are defined to be pairwise disjoint.
\end{itemize}

\begin{itemize}
	\item \textbf{{\em XKOS-C-DISJOINT-CLASSES-01:}} 
All \emph{XKOS} classes are defined to be pairwise disjoint.
\end{itemize}

@@

\subsection{Equivalent Properties*}

@@

\begin{itemize}
	\item \textbf{{\em DISCO-C-DATA-PROPERTY-FACETS-01:}} The abstract of a study (\emph{disco:purpose}) should have a minimum length (\emph{xsd:minLength}) of x. 
\end{itemize}

@@

\begin{itemize}
	\item \textbf{{\em DISCO-C-LITERAL-PATTERN-MATCHING-01:}} Each \emph{disco:Variable} of a given \emph{disco:LogicalDataSet} must have a given prefix for its variable name (\emph{skos:notation}). 
\end{itemize}

@@

\begin{DL}
Variable $\sqcup$ Question $\sqcup$ RepresentedVariable $\sqsubseteq$ $\forall$ concept.Concept \\
\end{DL}
\end{itemize}

@@

\subsection{Existential Quantifications*}

@@

\begin{itemize}
	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-01:}} 
There must be at least one {\em disco:universe} relationship from {\em disco:Studies} or {\em disco:StudyGroups} to {\em disco:Universe} (\ms{Study $\sqcup$ StudyGroup $\sqsubseteq$ $\exists$ universe.Universe}).
\end{itemize}

>>>>

We distinguish two validation types:
(1) \emph{Content-Driven Validation} $\mathcal{C}_{C}$ contains the set of constraints ensuring that the data is consistent with the intended syntax, semantics, and integrity of given data models.
(2) \emph{Technology-Driven Validation} $\mathcal{C}_{T}$ includes the set of constraints which can be generated automatically out of data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges.

@@

\begin{itemize}
  \item Constraint types marked with an asterisk (*) can be used as OWL 2 axioms. Thus, reasoners may be used to infer implicit triples resolving constraint violations caused when these constraints are validated.
	\item \underline{Underlined subsections} represent data model specific constraint types and do not correspond to RDF validation requirements (constraint types).
%	\item \underline{Underlined constraints} are part of content-driven validation.
%	\item \udash{Dashed underlined constraints} are part of technology-driven validation.
	\item $\mathcal{C}_{T}$ constraint types are marked with the superscript\textsuperscript{T}
	\item $\mathcal{C}_{C}$ constraint types are not marked
\end{itemize}

@@

\begin{itemize}
	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-01}}: 
	are compared variables represented in a compatible way, i.e. are the variables' code lists theoretically comparable?
		\begin{itemize}
		\item severity level: WARNING
	\end{itemize}
	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-02}}: 
	are variable definitions (\emph{dcterms:description}) available for each variable (\emph{disco:Variable}) to compare?
		\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-03}}:
	are code lists structured properly for each variable (\emph{disco:Variable}) to compare?
		\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-04}}:
	is for each code (for each variable (\emph{disco:Variable}) to compare) an associated category (a human-readable label) specified?
		\begin{itemize}
		\item severity level: INFO
	\end{itemize}
	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-05}}:
	each (\emph{disco:Variable}) to compare must be present.
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
\end{itemize}

@@

\begin{itemize}
	\item \textbf{{\em DISCO-C-DATA-MODEL-CONSISTENCY-01}}: 
	Codes (\emph{skos:Concept}) are ordered and therefore have fixed positions in an ordered collection (\emph{skos:OrderedCollection}) within a variable representation.
	The cumulative percentage of the current code is the cumulative percentage of the previous code (\emph{disco:cumulativePercentage})
	plus the percentage value (\emph{disco:percentage}) of the current code. 
		\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
	\item \textbf{{\em DISCO-C-DATA-MODEL-CONSISTENCY-02}}: 
	The cumulative percentage (\emph{disco:cumulativePercentage}) of the last code must be 100. 
		\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
	\item \textbf{{\em DISCO-C-DATA-MODEL-CONSISTENCY-03}}: 
	The number of valid cases (\emph{disco:SummaryStatistics} of the type (\emph{disco:summaryStatisticType}) \emph{ddicv-sumstats:ValidCases}) 
	for a particular variable must exactly be the sum of absolute frequencies of all valid cases (\emph{disco:inValid} of \emph{skos:Concept} is true).
		\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
	\item \textbf{{\em DISCO-C-DATA-MODEL-CONSISTENCY-04}}: 
	The number of invalid cases (\emph{disco:SummaryStatistics} of the type (\emph{disco:summaryStatisticType}) \emph{ddicv-sumstats:InvalidCases}) 
	for a particular variable must exactly be the sum of absolute frequencies of all invalid cases (\emph{disco:inValid} of \emph{skos:Concept} is false).
		\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
	\item \textbf{{\em DISCO-C-DATA-MODEL-CONSISTENCY-05}}: 
	The total number of valid and invalid cases (\emph{disco:SummaryStatistics} of the type (\emph{disco:summaryStatisticType}) \emph{ddicv-sumstats:NumberOfCases}) 
	for a particular variable must exactly be the number of valid cases plus the number of invalid cases.
		\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
	\item \textbf{{\em DISCO-C-DATA-MODEL-CONSISTENCY-06}}: 
	Some summary statistics types can only be calculated for given variable types. 
	It is not possible to compute minimum values for string variables.
		\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
	\item \textbf{{\em DISCO-C-DATA-MODEL-CONSISTENCY-07}}: 
	Some summary statistics types can only be calculated for given variable types. 
	It is not possible to compute mean values for categorical variables, only for metric variables.
		\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
\end{itemize}

@@

	\item \textbf{{\em SKOS-C-DATA-MODEL-CONSISTENCY-01\footnote{Corresponds to qSKOS Quality Issues - SKOS Semi-Formal Consistency Issues - Relation Clashes}:}}
	Relation Clashes:
  Covers condition S27 from the SKOS reference document, that has not been defined formally. 
	\begin{itemize}
	  \item Implementation:
		In a first step, all pairs of concepts are found that are associatively connected, using a SPARQL query. In the second step, a graph is created, containing only hierarchically related concepts and the respective relations. For each concept pair from the first step, we check for a path in the graph from step two. If such a path is found, a clash has been identified and the causing concepts are returned. 
		\item Severity level: INFO
	\end{itemize}

	\item \textbf{{\em SKOS-C-DATA-MODEL-CONSISTENCY-02\footnote{Corresponds to qSKOS Quality Issues - SKOS Semi-Formal Consistency Issues - Mapping Clashes}:}}
	Mapping Clashes:
  Covers condition S46 from the SKOS reference document, that has not been defined formally. 
	\begin{itemize}
	  \item Implementation:
		Can be solved by issuing a SPARQL query. 
		\item Severity level: INFO
	\end{itemize}

	\item \textbf{{\em SKOS-C-DATA-MODEL-CONSISTENCY-03\footnote{Corresponds to qSKOS Quality Issues - SKOS Semi-Formal Consistency Issues - Mapping Relations Misuse}:}}
	Mapping Relations Misuse:
  According to the SKOS reference documentation, mapping relations (e.g., \emph{skos:broadMatch} or \emph{skos:relatedMatch}) should be asserted to concepts being members of different concept schemes. This check finds concepts that are related by a mapping property and are either members of the same concept scheme or members of no concept scheme at all. 
	\begin{itemize}
		\item Severity level: INFO
	\end{itemize}

@@

\subsection{Subsumption*\textsuperscript{T}}

@@

\begin{itemize}
	\item \textbf{{\em DISCO-C-SUBSUMPTION-01:}} 
All {\em disco:Universe}s must also be {\em skos:Concept}s (\ms{Universe $\sqsubseteq$ Concept}).
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
\end{itemize}

\subsection{Class Equivalence*\textsuperscript{T}}

@@

\begin{itemize}
	\item \textbf{{\em DISCO-C-CLASS-EQUIVALENCE-01:}}
All {\em sio:SIO\_000367} resources must also be {\em disco:Variable}s (\ms{Variable $\equiv$ SIO\_000367}).
The Semanticscience Integrated Ontology (SIO)\footnote{https://code.google.com/p/semanticscience/wiki/SIO} provides a simple, integrated ontology of types and relations for rich description of objects, processes and their attributes.
{\em sio:SIO\_000367} is a variable defined as a value that may change within the scope of a given problem or set of operations.
Thus, {\em sio:SIO\_000367} is equivalent to {\em disco:Variable}.
\begin{itemize}
	\item severity level: INFO
\end{itemize}
\end{itemize}

\subsection{Sub Properties*\textsuperscript{T}}

@@

\begin{itemize}
	\item \textbf{{\em DISCO-C-SUB-PROPERTIES-01:}}
If an individual \emph{x} is connected by {\em disco:fundedBy} to an individual \emph{y}, then \emph{x} is also connected by {\em dcterms:contributor} to \emph{y} (\ms{fundedBy $\sqsubseteq$ contributor}). 
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
\end{itemize}

\subsection{Property Domains*\textsuperscript{T}}

@@

\subsection{Property Ranges*\textsuperscript{T}}

@@

\begin{itemize}
	\item \textbf{{\em DISCO-C-INVERSE-OBJECT-PROPERTIES-01}}:
	\emph{disco:CategoryStatistics} resources are accessed from codes (\emph{skos:Concept}s) via \emph{disco:statisticsCategory}$^{-}$.
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
	\item \textbf{{\em DISCO-C-INVERSE-OBJECT-PROPERTIES-02}}:
	\emph{disco:SummaryStatistics} resources are accessed from \emph{disco:Variable}s via \emph{disco:statisticsVariable}$^{-}$.
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
	\item \textbf{{\em DISCO-C-INVERSE-OBJECT-PROPERTIES-03}}:
	\emph{disco:Variable}s are accessed from \emph{disco:Question}s via \emph{disco:question}$^{-}$.
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
\end{itemize}

@@

\subsection{Asymmetric Object Properties*\textsuperscript{T}}

@@

\begin{itemize}
	\item \textbf{{\em DISCO-C-ASYMMETRIC-OBJECT-PROPERTIES-01:}} 
A {\em disco:Variable} may be based on a {\em disco:RepresentedVariable}.
A {\em disco:RepresentedVariable}, however, cannot be based on a {\em disco:Variable}.
This is a kind of mistake which may occur as a semantically equivalent object property for the other direction may also be possible ({\em disco:basisOf}) (\ms{$basedOn \sqcap basedOn^{-} \sqsubseteq \bot$}).
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
\end{itemize}

@@

\begin{itemize}
  \item \textbf{{\em DISCO-C-IRREFLEXIVE-OBJECT-PROPERTIES-01:}}
	In \emph{Disco}, every object property is irreflexive.
  No individual is connected by the object property {\em instrument} to itself (\ms{$\top$ $\sqsubseteq$ $\neg$ $\exists  instrument . Self$}).
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
\end{itemize}

@@

\begin{itemize}
  \item \textbf{{\em DISCO-C-CLASS-SPECIFIC-IRREFLEXIVE-OBJECT-PROPERTIES-01:}}
Within the Disco context, {\em skos:Concept}s cannot be related via the object property {\em skos:boader} to themselves (\ms{Concept $\sqsubseteq$ $\neg$$\exists$ broader.Self.}). 
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
	\item \textbf{{\em DISCO-C-CLASS-SPECIFIC-IRREFLEXIVE-OBJECT-PROPERTIES-02:}}
Within the Disco context, {\em skos:Concept}s cannot be related via the object property {\em skos:narrower} to themselves (\ms{Concept $\sqsubseteq$ $\neg$$\exists$ narrower.Self.}). 
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
\end{itemize}

\subsection{Disjoint Properties\textsuperscript{T}}

@@

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-DISJOINT-PROPERTIES-01:}} 
	All \emph{Data Cube} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
  The properties \emph{qb:dataSet} and \emph{qb:structure} are disjoint ($dataSet \sqsubseteq \neg structure$).
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DCAT-C-DISJOINT-PROPERTIES-01:}} 
	All \emph{DCAT} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DISCO-C-DISJOINT-PROPERTIES-01:}} 
	All \emph{Disco} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
  The properties \emph{disco:variable} and \emph{disco:question} are disjoint ($variable \sqsubseteq \neg question$).
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em PHDD-C-DISJOINT-PROPERTIES-01:}} 
	All \emph{PHDD} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
	The properties \emph{phdd:isStructuredBy} and \emph{phdd:column} are disjoint ($isStructuredBy \sqsubseteq \neg column$)
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
\end{itemize}

@@

	\item \textbf{{\em SKOS-C-DISJOINT-PROPERTIES-01:}} 
	All \emph{SKOS} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
	\item \textbf{{\em SKOS-C-DISJOINT-PROPERTIES-02\footnote{Corresponds to qSKOS Quality Issues - SKOS Semi-Formal Consistency Issues - Disjoint Labels Violation}:}}
	Disjoint Labels Violation:
  Covers condition S13 from the SKOS reference document stating that "\emph{skos:prefLabel}, \emph{skos:altLabel} and \emph{skos:hiddenLabel} are pairwise disjoint properties". 
	\begin{itemize}
	  \item Implementation:
		A SPARQL query collects all labels of all concepts, building an in-memory structure. This structure is then checked for disjoint entries. 
		\item severity level: ERROR
	\end{itemize}

@@

\begin{itemize}
	\item \textbf{{\em XKOS-C-DISJOINT-PROPERTIES-01:}} 
	All \emph{XKOS} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
\end{itemize}

\subsection{Disjoint Classes\textsuperscript{T}}

@@

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-DISJOINT-CLASSES-01:}} 
All \emph{Data Cube} classes are defined to be pairwise disjoint.
\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DCAT-C-DISJOINT-CLASSES-01:}} 
All \emph{DCAT} classes are defined to be pairwise disjoint.
\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em DISCO-C-DISJOINT-CLASSES-01:}} 
All \emph{Disco} classes are defined to be pairwise disjoint (e.g. \ms{Study $\sqcap$ Variable $\sqsubseteq$ $\perp$}).
\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em PHDD-C-DISJOINT-CLASSES-01:}} 
All \emph{PHDD} classes are defined to be pairwise disjoint.
\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em SKOS-C-DISJOINT-CLASSES-01:}} 
All \emph{SKOS} classes are defined to be pairwise disjoint.
\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item \textbf{{\em XKOS-C-DISJOINT-CLASSES-01:}} 
All \emph{XKOS} classes are defined to be pairwise disjoint.
\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
\end{itemize}

@@

\subsection{Equivalent Properties*\textsuperscript{T}}

@@

\begin{itemize}
	\item \textbf{{\em DISCO-C-DATA-PROPERTY-FACETS-01:}} The abstract of a series (\emph{dcterms:abstract}) should have a minimum length (\emph{xsd:minLength}) of some determined minimum length \emph{X}. 
	\begin{itemize}
		\item severity level: WARNING
	\end{itemize}
	\item \textbf{{\em DISCO-C-DATA-PROPERTY-FACETS-02:}} The abstract of a study (\emph{dcterms:abstract}) should have a minimum length (\emph{xsd:minLength}) of some determined minimum length \emph{X}. 
	\begin{itemize}
		\item severity level: WARNING
	\end{itemize}
\end{itemize}

@@

\begin{itemize}
	\item \textbf{{\em DISCO-C-LITERAL-PATTERN-MATCHING-01:}} Each \emph{disco:Variable} of a given \emph{disco:LogicalDataSet} must have a given prefix for its variable name (\emph{skos:notation}). 
	\begin{itemize}
		\item severity level: INFO
	\end{itemize}
\end{itemize}

@@

\begin{DL}
Variable $\sqcup$ Question $\sqcup$ RepresentedVariable $\sqsubseteq$ $\forall$ concept.Concept \\
\end{DL}
\begin{itemize}
	\item severity level: ERROR
\end{itemize}
\end{itemize}

@@

\subsection{Existential Quantifications*\textsuperscript{T}}

@@

	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-01:}} 
There must be at least one {\em disco:universe} relationship from {\em disco:StudyGroups} to {\em disco:Universe} (\ms{StudyGroup $\sqsubseteq$ $\exists$ universe.Universe}).
		\item severity level: ERROR
	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-02:}} 
There must be at least one {\em disco:universe} relationship from {\em disco:Studies} to {\em disco:Universe} (\ms{Study $\sqsubseteq$ $\exists$ universe.Universe}).
		\item severity level: ERROR
	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-03:}} 
There may be a {\em disco:universe} relationship from {\em disco:RepresentedVariable} to {\em disco:Universe} (\ms{RepresentedVariable $\sqsubseteq$ $\exists$ universe.Universe}).
		\item severity level: INFO
	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-04:}} 
There may be a {\em disco:universe} relationship from {\em disco:Variable} to {\em disco:Universe} (\ms{Variable $\sqsubseteq$ $\exists$ universe.Universe}).
		\item severity level: INFO
	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-05:}} 
There may be a {\em disco:universe} relationship from {\em disco:Question} to {\em disco:Universe} (\ms{Question $\sqsubseteq$ $\exists$ universe.Universe}).
		\item severity level: INFO
	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-06:}} 
There may be a {\em disco:universe} relationship from {\em disco:LogicalDataSet} to {\em disco:Universe} (\ms{LogicalDataSet $\sqsubseteq$ $\exists$ universe.Universe}).
		\item severity level: INFO
	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-07:}} 
  There is no relationship (\emph{disco:ddifile}) to a DDI-XML file containing further information about the series (\emph{disco:StudyGroup}) for further analyses.
		\item severity level: INFO
	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-08:}} 
  There is no relationship (\emph{disco:ddifile}) to a DDI-XML file containing further information about the study (\emph{disco:Study}) for further analyses.
		\item severity level: INFO
	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-09:}} 
  It is important to know the kind of data (\emph{disco:kindOfData}) collected for a particular series (\emph{disco:StudyGroup}).
	Survey data, e.g., is much easier accessible than census data. 
	For census data, it is necessary to get in contact with the individual data archive and if data access is granted it may take months to actually get the data.
		\item severity level: INFO
	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-10:}}
  It is important to know the kind of data (\emph{disco:kindOfData}) collected for a particular study (\emph{disco:Study}).
	Survey data, e.g., is much easier accessible than census data. 
	For census data, it is necessary to get in contact with the individual data archive and if data access is granted it may take months to actually get the data.
		\item severity level: INFO
	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-11:}} 
  Information about the temporal coverage (\emph{dcterms:temporal}) of a series (\emph{disco:StudyGroup}) is of interest for particular queries 
	(e.g. to search for all series of a given year (temporal coverage) and for which data is collected in which countries (spatial coverage) about which topics (topical coverage)).
		\item severity level: INFO
	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-12:}} 
  Information about the spatial coverage (\emph{dcterms:spatial}) of a series (\emph{disco:StudyGroup}) is of interest for particular queries 
	(e.g. to search for all series of a given year (temporal coverage) and for which data is collected in which countries (spatial coverage) about which topics (topical coverage)).
		\item severity level: INFO
	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-13:}} 
  Information about the topical coverage (\emph{dcterms:subject}) of a series (\emph{disco:StudyGroup}) is of interest for particular queries 
	(e.g. to search for all series of a given year (temporal coverage) and for which data is collected in which countries (spatial coverage) about which topics (topical coverage)).
		\item severity level: INFO
	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-14:}} 
  Information about the temporal coverage (\emph{dcterms:temporal}) of a study (\emph{disco:Study}) is of interest for particular queries 
	(e.g. to search for all studies of a given year (temporal coverage) and for which data is collected in which countries (spatial coverage) about which topics (topical coverage)).
		\item severity level: INFO
	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-15:}} 
  Information about the spatial coverage (\emph{dcterms:spatial}) of a study (\emph{disco:Study}) is of interest for particular queries 
	(e.g. to search for all studies of a given year (temporal coverage) and for which data is collected in which countries (spatial coverage) about which topics (topical coverage)).
		\item severity level: INFO
	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-16:}} 
  Information about the topical coverage (\emph{dcterms:subject}) of a study (\emph{disco:Study}) is of interest for particular queries 
	(e.g. to search for all studies of a given year (temporal coverage) and for which data is collected in which countries (spatial coverage) about which topics (topical coverage)).
		\item severity level: INFO
